Cost of Living in Toronto

### 2024-09-26 paper/paper.qmd
added sketches

```{r}
#| label: low-income-families4
#| fig-cap: "Table 4: Average Expenses of Low Income Households in Toronto"
#| echo: false

@@

```{r}
#| label: low-income-families5
#| fig-cap: "Average Expenses of Low Income Households in Toronto"
#| echo: false

@@

ggplot(data_long, aes(x = Household, y = Amount, fill = Type)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Figure 1: Total Income vs Total Expenses for Each Household", 
       x = "Household", 
       y = "Amount") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
Furthermore, `Figure 2` gives us a better understanding of the spending behind the high expenses. Rent was by far the most expensive, comprising 66% of the expenses.

>>>>

```{r}
#| label: low-income-families4
#| fig-cap: "Table 4: Differenece of Income and Expenses of Low Income Households in Toronto"
#| echo: false

@@

```{r}
#| label: low-income-families5
#| fig-cap: "Total Income and Expenses of Low Income Households in Toronto"
#| echo: false

@@

ggplot(data_long, aes(x = Household, y = Amount, fill = Type)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Figure 1: Total Income vs Total Expenses for Each Household", 
       x = "Household", 
       y = "Amount in $") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
Furthermore, `Figure 2` gives us a better understanding of the spending behind the high expenses. Rent was by far the most expensive, comprising 66% of the expenses.
